---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/leslie-huang/stylest.svg?branch=master)](https://travis-ci.org/leslie-huang/stylest) [![Build status](https://ci.appveyor.com/api/projects/status/384insyingv6jcg2?svg=true)](https://ci.appveyor.com/project/leslie-huang/stylest)

# stylest version 0.1.0

`stylest` estimates speaker style distinctiveness.

## Installation

Install `stylest` from CRAN by executing:


```{r eval = FALSE}
install.packages("stylest")
```

The dev version of `stylest` on GitHub may have additional features (and bugs) and is not guaranteed to be stable. Power users may install it with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
# devtools::install_github("leslie-huang/stylest")
```


See the <a href="https://github.com/leslie-huang/stylest/blob/master/vignettes/stylest-vignette.md">vignette</a> for examples and usage.

## Authors

<a href="http://leslie-huang.github.io">Leslie Huang (maintainer)</a>

<a href="https://github.com/patperry">Patrick O. Perry</a>

<a href="https://github.com/ArthurSpirling/">Arthur Spirling</a>

## Bug reports

Please submit any bugs, error reports, etc. on <a href="https://github.com/leslie-huang/stylest/issues">GitHub</a>.

